### 2013-07-24 doc/asplos14/evaluation.tex
scaling

The first group of four metrics relate to the communication
layer. Application messages refer to those issued by the user code;
network message refer to the aggregated packes sent over the wire. The
data show that most application messages are only a handful of bytes,
but our aggregator is able to turn them into packets of many kilobytes.

The next group of five metrics relate to the scheduler. We show the
average and maximum number of concurrently-executing tasks, along with
the average length of the ready queue and the average context switch
rate.  The last line shows the number of time a core stole work from
another core. Only UTS depends on work-stealing for performance; the
other applications exploit locality by binding tasks to specific cores
Nevertheless, even in UTS, which depends on work-stealing for
performance, steals are an infrequent occurance and account for a
small fraction of the execution time.

@@

\begin{figure}[ht]
    \begin{center}
      \includegraphics[height=0.5\textwidth]{results/plot_scaling.pdf}
    \end{center}
    \caption{Scaling for BFS, IntSort, and Pagerank. Refer to Figure~\cite{fig:grappa-gups} for GUPS scaling and Figure~\cite{fig:grappa-uts} for UTS scaling}
    \label{fig:grappa-scaling}
\end{figure}

Figures~\cite{fig:grappa-scaling}, \cite{fig:grappa-gups}, and
\cite{fig:grappa-uts} show scaling out to 64 nodes. Grappa scales best
on BFS and worst on IntSort, but is in general able to make use of
more nodes. Unfortunately memory limitations in our current network
library keep us from exploring scaling beyond 64 nodes; this will be
addressed in future work.

>>>>

The first group of four metrics relate to the communication
layer. Application messages refer to those issued by the user code;
network message refer to the aggregated packets sent over the wire. The
data show that most application messages are only a handful of bytes,
but our aggregator is able to turn them into packets of many kilobytes.

The next group of five metrics relate to the scheduler. We show the
average and maximum number of concurrently-executing tasks, along with
the average length of the ready queue and the average context switch
rate.  The last line shows the number of time a core stole work from
another core. Only UTS depends on work-stealing for performance; the
other applications exploit locality by binding tasks to specific cores
Nevertheless, even in UTS, which depends on work-stealing for
performance, steals are an infrequent occurrence and account for a
small fraction of the execution time.

@@

\begin{figure*}[ht]
    \begin{center}
      \subfloat[BFS]{ \includegraphics[height=0.25\textwidth]{results/plot_scaling_bfs.pdf} }\qquad
      \subfloat[IntSort]{ \includegraphics[height=0.25\textwidth]{results/plot_scaling_intsort.pdf} }\qquad
      \subfloat[Pagerank]{ \includegraphics[height=0.25\textwidth]{results/plot_scaling_pagerank.pdf} }\qquad
    \end{center}
    \caption{Scaling for BFS, IntSort, and Pagerank. Refer to Figure~\ref{fig:grappa-gups} for GUPS scaling and Figure~\ref{fig:grappa-uts} for UTS scaling}
    \label{fig:grappa-scaling}
\end{figure*}

Figures~\ref{fig:grappa-scaling}, \ref{fig:grappa-gups}, and
\ref{fig:grappa-uts} show scaling out to 64 nodes. Grappa scales best
on BFS and worst on IntSort, but is in general able to make use of
more nodes. Unfortunately memory limitations in our current network
library keep us from exploring scaling beyond 64 nodes; this will be
addressed in future work.
